---
title: "Plotly"
author: "Mariana Martins"
date: '18/08/2022'
format: revealjs
editor: visual
---

## Context

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Code

We are going to plot 'Mileage per gallon' vs 'Weight (1000 lbs)', by '\# of cylinders'

`library(plotly)`

`f <- list( family = "Courier New, monospace", size = 11,   color = "#6e6e6e" )`

`x <- list(title = "Weight (1000 lbs)",   titlefont = f )`

`y <- list( title = "Mileage per gallon",   titlefont = f )`

```{r}
library(plotly)
```

```{r include= TRUE}
f <- list(
  family = "Courier New, monospace",
  size = 11,   color = "#6e6e6e" )
x <- list(
  title = "Weight (1000 lbs)",   titlefont = f )

y <- list(
  title = "Mileage per gallon",   titlefont = f )
```

## Plotly code

`plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode="markers",   type="scatter",color=as.factor(mtcars$cyl), size=mtcars$hp ) %>%   layout(xaxis=x, yaxis=y)`

## Plotly Result

```{r include= TRUE}
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode="markers", 
        type="scatter",color=as.factor(mtcars$cyl), size=mtcars$hp ) %>%   
        layout(xaxis=x, yaxis=y)
```
